\plaintitle

### 2017-06-17 papers/IoT2017/intro.tex
comments and edits.

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive energy systems are
the next step for the smart grid.
% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.

@@

This paper assumes the existence of a distributed IoT infrastructure
and specifically focuses on the following privacy challenges:
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
 \Abhishek{Is this not
  related to the first point?  Perhaps the first point can be just
  about identity and second point can be specifically about
  consumption patterns.}\Aron{The first point is about to whom
  information might be leaked, and the second point is about the type
  of information. I'll make this more clear.}  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

\item \textbf{Pithy challenge summary needed.} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
  Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple energy usage data collected by smart
  meters.  More specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

@@

\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
  sure what you mean by ``such a service.''}  \Abhishek{We should
  connect the paper and our work back to IoT in this paragraph.}  This
paper proposes a solution that (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate the trading platform and enforce certain
safety rules.  \Aron{Since SIGCHI does not have section numbers, this
  paragraph, which describes the organization of the paper, is not
  very clear.}  We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  Next, we introduce a decentralized system for
transactive microgrids based on distributed ledgers and describe the
transactions and services used to implement this system.  We then
discuss how the system satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

>>>>

On one hand, transactive energy is a decentralized power system
controls problem \cite{7452738}, requiring strategic microgrid control
to maintain the stability of the community and the utility. On the
other hand, it is a distributed market problem where erroneous---as
well as malicious---transactions can create a gap between demand and
supply, eventually destabilizing the system. In both cases, however,
this system requires a distributed infrastructure comprising of smart
meters, feeders, smart inverters, utility substations, the utility
central offices, and the transmission system operator, which must
provide the necessary computation fabric to support the interplay
between the energy control and the fiscal market challenges.
Recently, demand-response systems have been enabled as applications of
IoT in smart grid~\cite{Haider2016166}. Transactive grid is the next step \cite{collier2017emerging}.
% With the advent of IoT-based solutions in smart-grid  dynamic demand response systems, which are a precursor to transactive sytems have been made possible.

@@

This paper assumes the existence of a distributed IoT infrastructure
and specifically focuses on the following privacy challenges:
%
%
% This is where the RIAPS and computing services discussion will be included. However, it does not solve the following challenges, which is the focus of this paper.
%
%\Abhishek{Can we merge this with last paragraph? It seems repetitive.}
%\Aron{I'll probably just remove this.}
%Specifically, 
%in order to take advantage of local energy production and storage capabilities, 
%in order to take advantage of these capabilities, 
%electric grids need to become more decentralized.
%However, a decentralized transactive energy system may pose a much greater threat to prosumers' privacy than existing smart metering systems.
%\Abhishek{We can introduce these bullets by stating that the privacy challenges specifically are (the privacy challenges were mentioned at the end of the paragraph above.)}
\begin{itemize}[itemsep=0.25\parskip,topsep=-0.5\parskip]
\item \textbf{Leakage of Energy Usage Patterns to Other Prosumenrs} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
 Since prosumers\footnote{We
  refer to customers as \emph{prosumers} to emphasize that they can
  not only consume energy, but may also produce it.} may purchase
  energy from each other in a transactive microgrid, transactions may
  inadvertently reveal the prosumers' detailed energy usage patterns
  to other prosumers within the microgrid.  Addressing this issue in a
  decentralized trading system is hard as it requires hiding the
  identities of trade partners from each other. In comparison, secure
  smart metering reveals the prosumers' energy usage patterns only to
  the operator.

\item \textbf{Preventing Inference of Future State of a Prosumer} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
 \Abhishek{Is this not
  related to the first point?  Perhaps the first point can be just
  about identity and second point can be specifically about
  consumption patterns.}\Aron{The first point is about to whom
  information might be leaked, and the second point is about the type
  of information. I'll make this more clear.}  Transactions may reveal
  the future energy usage of a prosumer, which could be used to infer
  private information.  For example, a smart home may know that its
  inhabitants will go out in the evening (\emph{e.g.}, by looking at
  their calendar), and it may trade energy futures accordingly in the
  morning.  Without adequate privacy measures, these trades may reveal
  to other prosumers in the microgrid that the inhabitants will not be
  at home later.  Note that energy
  futures, whose delivery may happen several hours after when the
  transaction is made, can play an important role in predicting and
  controlling microgrid load.  In comparison, smart metering reveals
  only current (or past) usage.

\item \textbf{Preventing Personally Identifiable Information} \Doug{Abhishek, can you please add a pithy summary of this challenge?}
  Transactions and energy
  usage data in a transactive microgrid are much richer sources of
  information than the simple energy usage data collected by smart
  meters.  More specifically, the information available in a
  transactive microgrid is a superset of what is available from smart
  metering, and it may be used to infer personal information, such as
  risk propensity and financial standing.
\end{itemize}
\vspace{0.5\parskip}

@@

In this paper, we describe an overview of the transactive sequence between different components of the systems. We also describe in the detail the structure of these transactions and show how these transactions  (1) enables trading energy futures in a
secure and verifiable manner, (2) preserves prosumer privacy, and (3)
enables DSOs to regulate the trading platform and enforce certain
safety rules.

%\Abhishek{Can we cite an example of such a service?}  \Aron{I am not
%  sure what you mean by ``such a service.''}  \Abhishek{We should
%  connect the paper and our work back to IoT in this paragraph.}  
  %This
%paper proposes a solution that (1) enables trading energy futures in a
%secure and verifiable manner, (2) preserves prosumer privacy, and (3)
%enables DSOs to regulate the trading platform and enforce certain
%safety rules. 
 %\Aron{Since SIGCHI does not have section numbers, this
 % paragraph, which describes the organization of the paper, is not
  %very clear.}

%\Abhishek{I have commented the previous because it seems redundant}
We first describe the basic components of a
transactive IoT microgrid and formulate security, safety, and privacy
requirements.  Next, we introduce a decentralized system for
transactive microgrids based on distributed ledgers and describe the
transactions and services used to implement this system.  We then
discuss how the system satisfies the security, safety, and privacy
requirements.  Finally, we give a brief overview of related work and
offer concluding remarks.

### 2017-06-17 papers/IoT2017/prelim.tex
comments and edits.

\section{Preliminaries and Requirements}
\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
This section describes the basic components of a transactive IoT
microgrid and formulates security, safety, and privacy requirements.

\subsection{Transactive Microgrid Components}

@@

\subsubsection{Microgrid Controller}
\Aron{Is this true?}
The microgrid controller stabilizes the load within the microgrid
based on the predicted future load within the microgrid and the rest
of the grid.  The controller first predicts load in the microgrid
based on (1) bids and asks in the bid storage and (2) outstanding
energy trades in the ledger.  By combining this information with the
prediction for the rest of the grid, the controller produces a control
signal that specifies how much the microgrid load should be decreased
or increased.  Based on this signal, the controller then updates the
price policy for the microgrid to influence energy production and
consumption.  We also assume the presence of a secondary controller
that balances voltage and frequency in the microgrid.

>>>>

%!TEX root = paper.tex
\section{Preliminaries and Requirements}
\Aron{Redundant, previous and following paragraphs state what we do here anyway.}
This section describes the basic components of a transactive IoT
microgrid and formulates security, safety, and privacy requirements.

\subsection{Transactive Microgrid Components}
\Abhishek{We need a figure here. We probably need to briefly describe a transactive energy architecture and then use that to set the requirements. The services described here will then better  fit in our section on solution }

@@

\subsubsection{Microgrid Controller (Distribution System Operator)}
\Aron{Is this true?}\Abhishek{I have editied it. We need to mention distribution system operator here.}
We assume the existence of a controller at the Distribution System Operator level that regulates the total load that the microgrid should present to the distribution system.
%The microgrid controller stabilizes the load within the microgrid
%based on the predicted future load within the microgrid and the rest
%of the grid. 
 The controller first predicts load in the microgrid
based on (1) bids and asks in the bid storage and (2) outstanding
energy trades in the ledger.  By combining this information with the
prediction for the rest of the grid, the controller produces a control
signal that specifies how much the microgrid load should be decreased
or increased.  Based on this signal, the controller then updates the
price policy for the microgrid to influence energy production and
consumption.  We also assume the presence of a secondary controller
that balances voltage and frequency in the microgrid.

### 2017-06-17 papers/IoT2017/solution.tex
comments and edits.

\section{Proposed System}

@@

\subsubsection{Energy Selling Process}
Consider a prosumer who wishes to sell energy to another
prosumer, as shown in Figure~\ref{fig:sellFlow}. 
As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.

>>>>

%!TEX root = paper.tex
\section{Proposed System}

@@

\subsubsection{Energy Selling Process}
Consider a prosumer who wishes to sell energy to another
prosumer, as shown in Figure~\ref{fig:sellFlow}\Abhishek{We need to mention what is the expected deadline by which this sequence of task should finish. }. 
As its first step, the prosumer withdraws an \emph{energy production asset} from its smart meter.
An energy production asset represents a permission to sell a certain amount of energy, and it is used to enforce safety requirements.
If the prosumer has sufficient unsold production capacity, the smart meter creates and transfers a production asset to the prosumer using a \emph{smart meter transaction} \circled{1}, which is recorded on the distributed ledger.

### 2017-06-17 papers/IoT2017/transactions.tex
comments and edits.

\subsection{Transactions}

In the previous subsection, we gave an overview of how transactions
are used in the trading process to transfer various assets.  We now
describe the format of these transactions, as well as the rules that
they have to satisfy to be valid and recorded on the ledger.  We also
introduce and detail the format of regulatory transactions, which the
DSO uses to regulate the microgrid.

>>>>

%!TEX root = paper.tex
\subsection{Transactions}

In the previous subsection, we gave an overview of how transactions
are used in the trading process to transfer various assets.  We now
describe the format of these transactions, as well as the rules that
they have to satisfy to be valid and recorded on the ledger.  We also
introduce and detail the format of regulatory transactions, which the
DSO uses to regulate the microgrid.\Abhishek{We need a figure describing the transactive system architecture. A collection of agents, arranged in a microgrid and a collection of microgrids being controlled by a DSO after the introduction}
